---
title: "Model s501 Test Data"
author: "JML"
date: "September 26, 2018 / January 25, 2021"
output: html_notebook
---

##Load Libraries (for AWS)
```{r}
packages <- c("haven", "tidyverse",
              "Matrix", "data.table", "dtplyr", "RSiena", "rmarkdown")
if (length(setdiff(packages, rownames(installed.packages()))) > 0) {
  install.packages(setdif(packagfes, rownames(installed.packages())))
}
lapply(packages, library, character.only = TRUE)
```

##Load or save workspace
```{r}
load("s501.RData")
```

```{r}
save.image("s501.RData")
```
# Model setup

#Create 2-wave s50 network 
Data from Scottish study of alc and tobacco use in adolescents
n=50
```{r}
mynet1 <- sienaDependent(array(c(s501, s502), dim=c(50, 50, 2)))
```

#Create s50 Alc Use variable
```{r}
s50a <- s50a[,1:2]
alcUse <- sienaDependent(s50a, type="behavior")
```

#s50 dataObj, effObj, algObj
```{r}
dataOb <- sienaDataCreate(mynet1, alcUse)
effOb <- getEffects(dataOb)
algOb <- sienaAlgorithmCreate(projname="s50Alc")
```
#s50 Add Effects
```{r}
effOb <- includeEffects(effOb, avAlt, interaction1="mynet1", type="eval",
                        name="alcUse", include=F)
effOb <- includeEffects(effOb, loPass, type = "eval",
                        name = "alcUse", include=F)
effOb <- includeInteraction(effOb, name = "alcUse", type = "eval",
                            avAlt, loPass,
                            interaction1 = c("mynet1", ""))
```
#Look at effects obj
```{r}
print(effOb, expand = TRUE) 
```

###Create HTML effects table
```{r}
effectsDocumentation(effOb, filename = "s50effx")
```

#Run model
```{r}
resOb <- siena07(algOb, data=dataOb, effects=effOb, batch=T)
```


#Calculate stats manually

###Center alcUse
```{r}
#Center the alc variable
s50a_c <- s50a - mean(s50a)
```

###avAlt statistic [verfified OK]
```{r}
#Calc av alt per individual
avAlt.vec <- s50a_c[,2] * gapply(s501, MARGIN=1, STATS=s50a_c[,2], FUN=mean, na.rm=T) 
#Remove NaNs (some egos chose no alters)
avAlt.vec <- ifelse(is.na(avAlt.vec), 0, avAlt.vec)
#Calculate the total statisic. Should be 33.57
avAlt.calc <- sum(avAlt.vec)
```

###Quad effect statistic [verified OK]
```{r}
#Should be 71.105
sum(s50a_c[,2]*s50a_c[,2])
```

###loPass effect statistic [verified OK]
```{r}
#Should be 24.1567
loPass.calc <- sum(1/(exp(s50a_c[,2])+1))
```

###loPass values for each individual 
```{r}
loPass.vec <- 1/(exp(s50a_c[,2])+1)
```

```{r}
s50a_c[,2]
```

###4loPass x avAlt statistic
This one is NOT correct. RSiena calculates this interaction to have
a statistic of -1.33
```{r}
discAvAlt <- sum(avAlt.vec * loPass.vec)
```

An alternative
```{r}
loPass.calc * 
```


